From Object Classification to Naming:\\ Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/acl2020_main.tex
[ACL2020] ...
small things, + a new final sentence in abstract on error analysis

%\usepackage{microtype}

@@

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\gbt}[1]{\textcolor{orange}{\emph{//gbt: #1//}}}
\newcommand{\cs}[1]{\textcolor{green!60!black}{\emph{//cs: #1//}}}
\newcommand{\mw}[1]{\textcolor{orange!60!black}{\emph{//mw: #1//}}}

% To streamline frequently used terms:
\newcommand{\langvis}{language\ \&\ vision\xspace}
\newcommand{\lv}{L\&V\xspace}
\newcommand{\mn}{ManyNames\xspace}
\newcommand{\mnshort}{MN\xspace}
\newcommand{\vg}{VisualGenome\xspace}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\sameobject}{SameObject\xspace}
\newcommand{\cluster}{Cluster\xspace}

@@

\title{From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects}

@@

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
%Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.
%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
\end{abstract}

>>>>

\usepackage{microtype}

@@

\iffalse
\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\gbt}[1]{\textcolor{orange}{\emph{//gbt: #1//}}}
\newcommand{\cs}[1]{\textcolor{green!60!black}{\emph{//cs: #1//}}}
\newcommand{\mw}[1]{\textcolor{orange!60!black}{\emph{//mw: #1//}}}
\fi
% To streamline frequently used terms:
\newcommand{\langvis}{language\ \&\ vision\xspace}
\newcommand{\lv}{L\&V\xspace}
\newcommand{\mn}{ManyNames\xspace}
\newcommand{\mnshort}{MN\xspace}
\newcommand{\vg}{VisualGenome\xspace}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\sameobject}{SameObject\xspace}
\newcommand{\cluster}{Cluster\xspace}

@@

\title{From Object Classification to Naming:\\ Modeling Entry-level Names for Real-world Objects}

@@

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
Our detailed error analysis reveals that models generally make more mistakes when human agreement is also low, with inadequate predictions due to bounding box issues being a major source of errors.
%Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.
%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
\end{abstract}

### 2019-12-10 papers/ACL2020/analysis.tex
small things, + a new final sentence in abstract on error analysis

Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. The proportion of human-like error is suprisingly constant across all models.
Both object detection models achieve essentially the same portion of human-like mishits. Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but fewer valid predictions, and also fewer nonsensical errors (other) compared to FRCNN$_{\text{VG1600}}$.
This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse invalid names that are semantically similar to a valid name.

>>>>

Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. 
The proportion of the human-like errors that related inadequate alternatives is surprisingly constant across all models.
Both object detection models achieve essentially the same portion of human-like mishits. Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits and also fewer nonsensical errors (other) compared to FRCNN$_{\text{VG1600}}$.
However, it also predicts fewer valid alternatives (SameObject).
This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse invalid names that are semantically similar to a valid name.

### 2019-12-10 papers/ACL2020/experiments.tex
small things, + a new final sentence in abstract on error analysis

We experiment with two kinds of (transferred) input features, different training vocabularies and ground-truth names for instances, similar to the detection models above.
This yields the following 5 transfer-learning-based naming models:
\begin{itemize}
\item FRCNN$_{\text{VG1600--VGMN}}$:
	This model extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{
	As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.
}. We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).  For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer. The model uses the VGMN vocabulary (overlap of the full ManyNames vocabulary with VG).
  \item ResNet-VGMN: 
For comparison, we consider a much less informed input, namely the features from the ResNet-101 image classification model, that was used to initialize the FRCNN models above, and pretrained on ImageNet \cite{imagenet_cvpr09}. 
Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names. The model uses the VGMN vocabulary.  The model is optimized on VG and MN ground truth names respectively.
 \item  ResNet-MN442:
 The same model as before, but trained with a vocabulary of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
\end{itemize}
Note that these five models are optimized on the $21$K~objects in \mn. 
To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.

>>>>

We experiment with two kinds of (transferred) input features, different training vocabularies and ground-truth names for instances, similar to the detection models above.
This yields the following 5 transfer-learning-based naming models:
\begin{itemize}
\item FRCNN$_{\text{VG1600--VGMN}}$:
	This model extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{
	As experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former.
}. We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).  For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer. The model uses the VGMN vocabulary (overlap of the full ManyNames vocabulary with VG).
  \item ResNet-VGMN: 
For comparison, we consider a much less informed input, namely the features from the ResNet-101 image classification model, that was used to initialize the FRCNN models above, and pretrained on ImageNet \cite{imagenet_cvpr09}. 
Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names. The model uses the VGMN vocabulary.  The model is optimized on VG and MN ground truth names respectively.
 \item  ResNet-MN442:
 The same model as before, but trained with a vocabulary of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
\end{itemize}
Note that these five models are optimized on the $21$K~objects in \mn. 
To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.

### 2019-12-10 papers/ACL2020/manynames.tex
small things, + a new final sentence in abstract on error analysis

Regarding (i), recall that a traditional view of object naming regards all instances of a class to have the same entry-level name.
We observe instead that many pairs of entry-level names do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
%% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name---a strict requirement which only 281 of the 442 entry-level names of \mn meet.
These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
%% SHORTENING %%  (SD: .34).
Importantly, the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).

>>>>

Regarding (i), recall that a traditional view of object naming regards all instances of a class to have the same entry-level name.
We observe instead that many pairs of entry-level names do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
%% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name---a strict requirement which only 281 of the 442 entry-level names of \mn meet.
These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
%% SHORTENING %%  (SD: .34).
Importantly, the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, they is still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).

### 2019-12-10 papers/ACL2020/related.tex
small things, + a new final sentence in abstract on error analysis

%\paragraph{(Entry-Level) Object Naming}
%cognitive science/psychology:\\
%- levels of specificity\\
%- basic-level vs. entry-level\\ 
%- object naming studies
%
%Language + Vision:\\
%Ordonez et al., Zarriess \& Schlangen, ... \\
%- Our work: empirical notion of entry-level
%\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
%% SHORTENING %%Our work on natural object naming connects research in psycholinguistics, \langvis and computer vision. 
In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
The typicality of the object with respect to this basic-level is important for determining the preferred name, i.e.\ the entry-level name: typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific \category.
%% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
\newcite{Ordonez:2016} adopt this and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
By contrast, we use \mn (details below) to directly test and fine-tune object recognition (and image classification) systems, without presupposing a taxonomical relationship between the possible names for an object.

>>>>

%\paragraph{(Entry-Level) Object Naming}
%cognitive science/psychology:\\
%- levels of specificity\\
%- basic-level vs. entry-level\\ 
%- object naming studies
%
%Language + Vision:\\
%Ordonez et al., Zarriess \& Schlangen, ... \\
%- Our work: empirical notion of entry-level
%\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
%% SHORTENING %%Our work on natural object naming connects research in psycholinguistics, \langvis and computer vision. 
In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
The typicality of the object with respect to this basic-level is important for determining the preferred name, i.e.\ the entry-level name: typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific \category.
%% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
\newcite{Ordonez:2016} adopt this and train a model to map an object's \category detected by an object recognition system to a name, guided by external resources like corpus statistics.
By contrast, we use \mn (details below) to directly test and fine-tune object recognition (and image classification) systems, without presupposing a taxonomical relationship between the possible names for an object.
